Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection Fourier transform Mass Spectrometry Experiments

### 2022-04-12 doc/peakcharacterization_manuscript.Rmd
closes #23

::: {custom-style="MDPI_5.2_figure"}
```{r nap_intensity, dn_id = figure_count, fig.width = 16, fig.height = 8}
nap_fontsize = 12
tar_load(aa_diffs_filtersd_1ecf)
tar_load(aa_diffs_filtersd_2ecf)

>>>>

::: {custom-style="MDPI_5.2_figure"}
```{r nap_intensity, dn_id = figure_count, fig.width = 16, fig.height = 8}
nap_fontsize = 10
tar_load(aa_diffs_filtersd_1ecf)
tar_load(aa_diffs_filtersd_2ecf)
